Social Computing Article\thanks{This title is temporary}

### 2013-01-14 Article.tex
mexi um pouco nos resultados e arrumei algumas coisas ao longo do texto

We have built a multi-agent system that simulates the experiments of~\cite{farenzena:collabem}, using the model of human behaviour proposed by them. We adapted that behaviour into a set of rules which we modeled in the \emph{Memetic Network} model proposed by~\cite{araujo:memenet}. For simplicity, we limited our experiments to the Sudoku problem. Our goal is verifying whether the strategies employed by humans are competitive with other heuristics. After identifying the points in which those are lacking, we will then propose methods to increase the efficiency of human problem-solving networks.

@@

We developed a system in which the environment of the {\em Sudoku} problem-solving social network presented in~\cite{farenzena:collabem} could be modelled through autonomous agent networks and analysed through a series of experiments. We conceived a novel method for agent-based social problem solving witch draws inspiration from the optimization technique of {\em Memetic Networks}~\cite{araujo:memenet}.

@@

~\cite{farenzena:collabem} have stated that, in their settings, {\em "cooperation works because agents can copy each other"}. Our experiments indicate that, indeed, in some of the topologies tested, the {\em copy rate} has a decisive role in enhancing the algorithm's performance (see Figure 2 and Figure 3). The graphs in Figure 2 and Figure 3 - in which the vertical axis represents the number of iterations needed for the agents to solve the problem - both show a peak in ({\em copy rate}: 7, {\em guess rate}: 0) and a valley in ({\em copy rate}: 87, {\em guess rate}: 100), indicating that the greater the {\em copy} and {\em guess} rates are, the fewer iterations are needed for the agents to solve the problem. We understand this is due to the fact that some agents of low levels are incapable of solving some instances of the {\em Sudoku} problem, don't knowing the {\em Sudoku} solving rules needed to mark its cells. These agents have no hope solving the problem without some guessing mechanism, and take advantage of high {\em copy rates}, which can be used to correct wrong guesses through copying better agent's solutions.

@@

Of the three metric employed by us in the \emph{Social Stage}, only one had the agent evaluate the content of the solutions proposed by their neighbours. The other chose who to copy based on position, simulating observed human behaviour, and the remaining one chose a neighbour randomly. Our experiments have shown that evaluating the proposed solutions indeed bring significantly better results, despite the fact that humans seemingly avoid that strategy. In all topologies, choosing the solution with the largest number of filled cells not only allows agents to solve the instance earlier, but also causes the network to converge faster to the correct solution. That is, once one individual has found the correct solution, that solution spreads faster through the network if the other agents are evaluating the solutions that reach them.

>>>>

We have developed and detailed a novel method for agent-based social problem solving which draws inspiration from the {\em Memetic Networks} model proposed by~\cite{araujo:memenet}. It was used it to built a multi-agent system that simulates the experiments of~\cite{farenzena:collabem}, using the model of human behaviour proposed by them. For simplicity, we limited our experiments to the {\em Sudoku} problem. Our goal is verifying whether the strategies employed by humans are competitive with other heuristics. After identifying the points in which those are lacking, we will then propose methods to increase the efficiency of human problem-solving networks.

@@

We developed a system in which the environment of the {\em Sudoku} problem-solving social network presented in~\cite{farenzena:collabem} could be modelled through autonomous agent networks and analysed through a series of experiments. We conceived a novel method for agent-based social problem solving which draws inspiration from the optimization technique of {\em Memetic Networks}~\cite{araujo:memenet}.

@@

Farenzena ~\cite{farenzena:collabem} have stated that, in their settings, {\em "cooperation works because agents can copy each other"}. Our experiments indicate that, indeed, in some of the topologies tested, the {\em copy rate} has a decisive role in enhancing the algorithm's performance (see Figure 2 and Figure 3). The graphs in Figure 2 and Figure 3 - in which the vertical axis represents the number of iterations needed for the agents to solve the problem - both show a peak in ({\em copy rate}: 7, {\em guess rate}: 0) and a valley in ({\em copy rate}: 87, {\em guess rate}: 100), indicating that the greater the {\em copy} and {\em guess} rates are, the fewer iterations are needed for the agents to solve the problem. We understand this is due to the fact that some agents of low levels are incapable of solving some instances of the {\em Sudoku} problem, don't knowing the {\em Sudoku} solving rules needed to mark its cells. These agents have no hope solving the problem without some guessing mechanism, and take advantage of high {\em copy rates}, which can be used to correct wrong guesses through copying better agent's solutions. Also, as shown in Figure 4, there is a correlation between the copy and guess rates and the convergence of the algorithm: the greater they are, the greater is the probability that the agent network will be able to solve the problem.

@@

Of the three metrics employed by us in the \emph{Social Stage}, only one had the agent evaluate the content of the solutions proposed by their neighbours. The other chose who to copy based on position, simulating observed human behaviour, and the remaining one chose a neighbour randomly. Our experiments have shown that evaluating the proposed solutions indeed bring significantly better results, despite the fact that humans seemingly avoid that strategy. In all topologies, choosing the solution with the largest number of filled cells not only allows agents to solve the instance earlier, but also causes the network to converge faster to the correct solution. That is, once one individual has found the correct solution, that solution spreads faster through the network if the other agents are evaluating the solutions that reach them.
